---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r}
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))
```

```{r}
library(tidyverse)
library(dplyr)
library(tidyjson)
library(Cairo)
```
```{r}
cairo = !F
```
## Collect Data

Set Up Paths
```{r}
#batches_nums = 4:6
#batches_nums = 5:6
#batches_nums = 6
#batches_nums = 8
batches_nums = 9

batches_paths = lapply(batches_nums, function (t) paste("../batches/batch_",t, sep=""))
path_mzn = "outputs_mzn"
path_lp  = "outputs_lp"

listBatchFiles =
  function (batch_path, target_dir) {
    dir_path = paste(batch_path,target_dir, sep="/")
    dir_files = list.files(dir_path, pattern = "*.json")
    lapply(dir_files, function(t) paste(batch_path,target_dir,t, sep="/"))
  }

mzn_files =
  unlist(
    lapply(
      batches_paths,
      function (p) listBatchFiles(p, path_mzn)
    )
  )

lp_files =
  unlist(
    lapply(
      batches_paths,
      function (p) listBatchFiles(p, path_lp)
    )
  )
```

Load data

```{r}
#TIMEOUT_time = 2.5*60 # seconds
#TIMEOUT_time = 5*60 + 20 # seconds
TIMEOUT_time = 5*60 - 3.0 # seconds

tabelFromFiles = function (files, timeoutToTime=F, timeToTimeout=F) {
  data =
    files %>% 
    map_df(
      function(t)
        read_json(t) %>%
        spread_all() %>%
        as_tibble() %>%
        select(-document.id)
    ) %>%
    #select(-sol) %>%
    mutate(file_path=unlist(files)) %>%
    mutate(num = row_number() - 1) %>%
    select(num, file_path, everything())
  
  data =
    data %>%
    mutate(batch     = lapply(data$file_path, FUN=function(t) as.character(unlist(strsplit(t, "/")[[1]][[3]])))) %>%
    mutate(file_name = lapply(data$file_path, FUN=function(t) as.character(unlist(strsplit(t, "/")[[1]][[5]])))) # %>%
  
  if (timeToTimeout) {
    data =
      data %>%
      mutate(timeouted = solveTime >= TIMEOUT_time) %>%
      mutate(timeouted = time >= TIMEOUT_time)
  }
  if (timeoutToTime) {
    data =
      data %>%
      mutate(time = ifelse(timeouted, TIMEOUT_time, time)) %>%
      mutate(solveTime = ifelse(timeouted, TIMEOUT_time, solveTime))
  }
  return(data)
}

mzn_data = tabelFromFiles(mzn_files, T,!T)
#View(mzn_data)

lp_data = tabelFromFiles(lp_files, T,!T)
#View(lp_data)


intersect_cols = intersect(names(lp_data), names(mzn_data))
data = rbind(
  mzn_data %>% select(all_of(intersect_cols)),
  lp_data  %>% select(all_of(intersect_cols))
  )

if (TIMEOUT_time <= max(max(data$time), max(data$solveTime))) {
  #TIMEOUT_time = max(max(data$time), max(data$solveTime)) + 10
  TIMEOUT_time = max(max(data$time), max(data$solveTime))
  mzn_data =
    mzn_data %>%
    mutate(time      = ifelse(timeouted, TIMEOUT_time, time)) %>%
    mutate(solveTime = ifelse(timeouted, TIMEOUT_time, solveTime))
  
  lp_data =
    lp_data %>%
    mutate(time      = ifelse(timeouted, TIMEOUT_time, time)) %>%
    mutate(solveTime = ifelse(timeouted, TIMEOUT_time, solveTime))
  
   mzn_data = mzn_data %>% select(all_of(intersect_cols))
   lp_data = lp_data  %>% select(all_of(intersect_cols))
  
  data = rbind(
    mzn_data,
    lp_data
  )
}
#View(data)
```

Create data for H and K (without reading inputs)
```{r}
K_max = H_max = 10

inputs =
  data.frame(
    num = 1:(K_max*H_max),
    K = rep(1:K_max, each=K_max),
    H = rep(1:H_max, K_max)
  ) %>% gather("K", "H", key = "type", value = "val") 

if (cairo){ Cairo(900, 700, file="input_sizes.png", type="png", bg="white") }
inputs %>%
  ggplot(aes(x=num, y = val, fill = type)) + # , alpha=0.1)) +
  #geom_bar(stat="identity", show.legend = F)
  #geom_bar(stat="identity", alpha=0.9, show.legend = F) +
  #geom_bar(stat="identity", alpha=0.9) +
  geom_bar(stat="identity", alpha=0.9, position = position_dodge()) +
  xlab("Numero Input") +
  ylab("Value") +
  scale_fill_discrete(name="")

#inputs_bars =
#  geom_bar(data=inputs, mapping=aes(x=num, y=-val, color=type, alpha=0.1), stat="identity", show.legend = F)

# ) %>% mutate(KxH=K*H)
#if (cairo){ Cairo(900, 700, file="input_sizes.png", type="png", bg="white") }
#inputs %>%
#  ggplot(aes(x=num, y = -KxH)) +
#  geom_bar(stat="identity") #+
#  #scale_fill_discrete(c("ff0000", "00ff00"))
#
##inputs_bars =
##  geom_bar(data=inputs, mapping=aes(x=num, y=-KxH), stat="identity", show.legend = F)
```

First plot
```{r}
mzn_timeouted =
  data %>%
    filter(timeouted) %>%
    filter(model_type == 'MZN')

lp_timeouted =
  data %>%
    filter(timeouted) %>%
    filter(model_type == 'LP')

if (cairo){ Cairo(900, 700, file="first_plot.png", type="png", bg="white") }
plot1 =
  data %>%
  ggplot(aes(x=num, y=solveTime, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(mzn_timeouted, mapping=aes(x=num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_timeouted,  mapping=aes(x=num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  #geom_bar(data=inputs, mapping=aes(x=num, y=-val, color=type, fill=type, alpha=0.1), stat="identity", show.legend = F) # +
  #geom_line(data=inputs, mapping=aes(x=num, y=-KxH-10, color="green"), show.legend = F) #+
  #geom_bar(data=inputs, mapping=aes(x=num, y=-KxH, color=""), stat="identity", show.legend = F) #+
  xlab("Numero Input") +
  ylab("Tempo di Risoluzione (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc"))
plot1

if (cairo){ Cairo(900, 700, file="second_plot.png", type="png", bg="white") }
plot2 =
  data %>%
  ggplot(aes(x=num, y=time, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(mzn_timeouted, mapping=aes(x=num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_timeouted,  mapping=aes(x=num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  #geom_bar(data=inputs, mapping=aes(x=num, y=-val, color=type, fill=type, alpha=0.1), stat="identity", show.legend = F) # +
  xlab("Numero Input") +
  ylab("Tempo Totale (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) # legenda
plot2

require(gridExtra)
if (cairo){ Cairo(900*2, 700, file="third_plot.png", type="png", bg="white") }
grid.arrange(plot1, plot2, ncol=2)
```
```{r}
## ## WIP
## data %>%
##   filter(num < 30) %>%
##   ggplot(aes(x=num, y=solveTime, color=model_type)) +
##   #geom_bar(data=inputs %>% filter(num<30), mapping=aes(x=num, y=-KxH, color="zz", fill="zz"), stat="identity", show.legend = F) +
##   #ggplot(aes(x=num, y=solveTime)) +
##   geom_line() +
##   #geom_point(mzn_timeouted, mapping=aes(x=num, y=rep(TIMEOUT_time +  5,nrow(mzn_timeouted)), color=model_type), show.legend = F) +
##   #geom_point(lp_timeouted,  mapping=aes(x=num, y=rep(TIMEOUT_time + 10,nrow(lp_timeouted )), color=model_type), show.legend = F) +
##   #geom_bar(data=inputs %>% filter(num < 30), mapping=aes(x=num, y=-val, color=type, fill=type, alpha=0.1), stat="identity", show.legend = F) # +
##   geom_line(data=inputs %>% filter(num < 30), mapping=aes(x=num, y=-KxH, color="green"), show.legend = F) # +
## 
## ggplot() + 
##   geom_bar(mapping = aes(x = dt$when, y = dt$numinter), stat = "identity", fill = "grey") +
##   geom_line(mapping = aes(x = dt$when, y = dt$prod*5), size = 2, color = "blue") + 
##   scale_x_date(name = "Day", labels = NULL) +
##   scale_y_continuous(name = "Interruptions/day", 
##     sec.axis = sec_axis(~./5, name = "Productivity % of best", 
##       labels = function(b) { paste0(round(b * 100, 0), "%")})) + 
##   theme(
##       axis.title.y = element_text(color = "grey"),
##       axis.title.y.right = element_text(color = "blue"))
```


## Sorted By mzn time

```{r}
sorted_mzn_data = mzn_data %>%
  arrange(time) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())

sorted_lp_data = lp_data %>%
  arrange( order(sorted_mzn_data$num) ) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())
  
  
time_sorted_data = rbind(sorted_mzn_data, sorted_lp_data)
#View(time_sorted_data)
```


```{r}
mzn_timeouted =
  time_sorted_data %>%
    filter(timeouted) %>%
    filter(model_type == 'MZN')

lp_timeouted =
  time_sorted_data %>%
    filter(timeouted) %>%
    filter(model_type == 'LP')

if (cairo){ Cairo(600, 600, file="solveTimes.png", type="png", bg="white") }
time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=solveTime, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(mzn_timeouted, mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_timeouted,  mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  xlab("Numero Input (mzn time order)") +
  ylab("Tempo di Risoluzione (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
    

if (cairo) { Cairo(600, 600, file="times.png", type="png", bg="white") }
time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=time, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(mzn_timeouted, mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_timeouted,  mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  xlab("Numero Input (mzn time order)") +
  ylab("Tempo Totale (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
```
## Sorted By lp time

```{r}
lp_sorted_lp_data = lp_data %>%
  arrange(time) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())

lp_sorted_mzn_data = mzn_data %>%
  arrange( order(lp_sorted_lp_data$num) ) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())
  
  
lp_time_sorted_data = rbind(lp_sorted_mzn_data, lp_sorted_lp_data)
#View(lp_time_sorted_data)
```


```{r}
lp_mzn_timeouted =
  lp_time_sorted_data %>%
    filter(timeouted) %>%
    filter(model_type == 'MZN')

lp_lp_timeouted =
  lp_time_sorted_data %>%
    filter(timeouted) %>%
    filter(model_type == 'LP')

if (cairo){ Cairo(900, 700, file="sorted_lp_time_solveTimes.png", type="png", bg="white") }
lp_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=solveTime, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(lp_mzn_timeouted, mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_lp_timeouted,  mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  xlab("Numero Input (lp time order)") +
  ylab("SolveTime (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
    

if (cairo) { Cairo(900, 700, file="sorted_lp_time_times.png", type="png", bg="white") }
lp_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=time, color=model_type)) +
  #geom_line() +
  geom_point(shape="circle", alpha=0.7) +
  geom_point(lp_mzn_timeouted, mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 15,nrow(mzn_timeouted)), color=model_type), show.legend = F, shape="triangle") +
  geom_point(lp_lp_timeouted,  mapping=aes(x=sorted_num, y=rep(TIMEOUT_time + 20,nrow(lp_timeouted )), color=model_type), show.legend = F, shape="triangle") +
  
  xlab("Numero Input (lp time order)") +
  ylab("Tempo Totale (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
```

## Sorted By lp time timouted removed

```{r}
tr_sorted_lp_data = lp_data %>%
  filter(! lp_data$timeouted) %>%
  arrange(time) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())

tr_sorted_mzn_data = mzn_data %>%
  filter(! lp_data$timeouted) %>%
  arrange( order(tr_sorted_lp_data$num) ) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())
  
  
tr_time_sorted_data = rbind(tr_sorted_mzn_data, tr_sorted_lp_data)
#View(tr_time_sorted_data)
```


```{r}
if (cairo) { Cairo(900, 700, file="sorted_lp_time_no_timeout_solveTimes.png", type="png", bg="white") }
plot1 =
tr_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=solveTime, color=model_type)) +
  #geom_line(alpha=0.7) +
  geom_point(shape="circle", alpha=0.7) +
  xlab("Numero Input (lp time order)") +
  ylab("Tempo di Risoluzione (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
plot1

if (cairo) { Cairo(900, 700, file="sorted_lp_time_no_timeout_times.png", type="png", bg="white") }
plot2 =
tr_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=time, color=model_type)) +
  #geom_line(alpha=0.7) +
  geom_point(shape="circle", alpha=0.7) +
  xlab("Numero Input (lp time order)") +
  ylab("Tempo Totale (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
plot2


require(gridExtra)
if (cairo){ Cairo(900*2, 700, file="sorted_lp_time_no_timeout_both.png", type="png", bg="white") }
grid.arrange(plot1, plot2, ncol=2)
```



## Sorted By lp solveTime timouted removed

```{r}
tr_sorted_lp_data = lp_data %>%
  filter(! lp_data$timeouted) %>%
  arrange(solveTime) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())

tr_sorted_mzn_data = mzn_data %>%
  filter(! lp_data$timeouted) %>%
  arrange( order(tr_sorted_lp_data$num) ) %>%
  mutate(sorted_num = row_number() - 1) %>%
  select(sorted_num, num, everything())
  
  
tr_time_sorted_data = rbind(tr_sorted_mzn_data, tr_sorted_lp_data)
#View(tr_time_sorted_data)
```


```{r}
if (cairo) { Cairo(900, 700, file="sorted_lp_solveTime_no_timeout_solveTimes.png", type="png", bg="white") }
plot1 =
tr_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=solveTime, color=model_type)) +
  #geom_line(alpha=0.7) +
  geom_point(shape="circle", alpha=0.7) +
  xlab("Numero Input (lp time order)") +
  ylab("Tempo di Risoluzione (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
plot1

if (cairo) { Cairo(900, 700, file="sorted_lp_solveTime_no_timeout_times.png", type="png", bg="white") }
plot2 =
tr_time_sorted_data %>%
  ggplot(aes(x=sorted_num, y=time, color=model_type)) +
  #geom_line(alpha=0.7) +
  geom_point(shape="circle", alpha=0.7) +
  xlab("Numero Input (lp time order)") +
  ylab("Tempo Totale (s)") +
  scale_colour_discrete(name="Modello", labels=c("ASP", "Minizinc")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank()
    )
plot2

require(gridExtra)
if (cairo){ Cairo(900*2, 700, file="sorted_lp_solveTime_no_timeout_both.png", type="png", bg="white") }
grid.arrange(plot1, plot2, ncol=2)
```

## Analisi

* Numero di timeout
* quante volte LP e' migliore di MZN
* Ordinare dati per H + K

# Numero Timeout
```{r, show=F}
timeout_count =
  data %>%
  group_by(model_type) %>%
  filter(timeouted) %>%
  count(timeouted) %>%
  select(-timeouted)

show( paste (
  "MZN va in timeout",
  timeout_count %>% filter(model_type == 'MZN') %>% pull(n),
  "volte su",
  nrow(data %>% filter(model_type == 'MZN')),
  "(",
  timeout_count %>% filter(model_type == 'MZN') %>% pull(n) / nrow(data %>% filter(model_type == 'MZN')) * 100, 
  "%)"
  )
)
show( paste (
  "LP va in timeout",
  timeout_count %>% filter(model_type == 'LP') %>% pull(n),
  "volte su",
  nrow(data %>% filter(model_type == 'LP')),
  "(",
  timeout_count %>% filter(model_type == 'LP') %>% pull(n) / nrow(data %>% filter(model_type == 'LP')) * 100, 
  "%)"
  )
)
```
# Quante volte MZN e' migliore di LP (time)
```{r, show=F}
time_wins_count =
  mzn_data %>%
  select(-file_path, -sol.H, -sol.K, -num) %>%
  inner_join(lp_data, by=c("batch","file_name"), suffix=c(".mzn", ".lp")) %>%
  select(-file_path, -sol.H, -sol.K) %>%
  select(num, batch, file_name, sat.mzn, sat.lp, everything()) %>%
  count(mzn_wins=time.mzn < time.lp)

time_wins_count

show( paste (
  "MZN batte sul tempo complessivo LP",
  time_wins_count %>% filter(mzn_wins) %>% pull(n),
  "volte",
  "(",
  time_wins_count %>% filter(mzn_wins) %>% pull(n) / sum(time_wins_count$n) * 100, 
  "%)"
  )
)

```


# Quante volte MZN e' migliore di LP (solveTime)
```{r, show=F}
solveTime_wins_count =
  mzn_data %>%
  select(-file_path, -sol.H, -sol.K, -num) %>%
  inner_join(lp_data, by=c("batch","file_name"), suffix=c(".mzn", ".lp")) %>%
  #select(-file_path, -sol.H, -sol.K) %>%
  #select(num, batch, file_name, sat.mzn, sat.lp, everything()) %>%
  select(solveTime.mzn, solveTime.lp) %>%
  count(mzn_wins=solveTime.mzn < solveTime.lp)

time_wins_count

show( paste (
  "MZN batte sul solveTime LP",
  solveTime_wins_count %>% filter(mzn_wins) %>% pull(n),
  "volte",
  "(",
  solveTime_wins_count %>% filter(mzn_wins) %>% pull(n) / sum(time_wins_count$n) * 100, 
  "%)"
  )
)

```












































